Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-05-19 paper/ms.tex
Update bar decomp figure

\begin{figure*}[t!]%
\centering
\includegraphics[width=18cm]{fig/fig-bar_decomp.pdf}
\caption{\textbf{Disk decomposition into the bar and unbarred disk.} This
procedure is based on ref.\cite{2016MNRAS.463.1952P} The \textit{left panel}
shows a surface density projection through the stellar component of the
\Nbody{} simulation (disk and bulge). The \textit{middle panel} shows the
component of the disk identified as being trapped in the bar while the
\textit{right panel} shows the component of the disk identified as not being
trapped in the bar. The fact that the untrapped stars form a roughly
axisymmetric structure indicates our bar decomposition is sufficiently
accurate. {\color{red} I will remake this figure
- I ended up losing the files which stored the bar membership, so I just
pulled these screenshots from an earlier presentation.}}
\label{fig:decomp}
\end{figure*}

>>>>

\begin{figure*}[t!]%
\centering
\includegraphics[width=18cm]{fig/fig-bar.pdf}
\caption{\textbf{Disk decomposition into the bar and unbarred disk.} This
procedure is based on ref.\cite{2016MNRAS.463.1952P} The \textit{left panel}
shows a surface density projection through the stellar component of the
\Nbody{} simulation (disk and bulge). The \textit{middle panel} shows the
component of the disk identified as being trapped in the bar while the
\textit{right panel} shows the component of the disk identified as not being
trapped in the bar. The fact that the untrapped stars form a roughly
axisymmetric structure indicates our bar decomposition is sufficiently
accurate.}
\label{fig:decomp}
\end{figure*}
